### 2014-10-26 thesis/method/evaluation.tex
Update evaluation section

\subsection{Statistical Tests}
To decide whether or not the difference in values of each measure between
classifiers and feature selection methods was statistically significant,
paired $t$-tests at a significance level of 0.05 were conducted.

\section{Summary}

>>>>

\subsection{Tests for Statistical Significance}
To decide whether or not the difference in values of each measure between
classifiers and feature selection methods was statistically significant,
paired $t$-tests at a significance level of 0.05 were conducted.
\todo{elaborate}

\section{Summary}
In this section we described our method of evaluating the performance of each
classifier and feature selection method that we use. We used accuracy and the
area under the curve to measure two different aspects of our classifiers, and
we obtained these figures using stratified ten-fold cross-validation. Paired
$t$-tests were conducted to test for statistical significance.
